Sparse Function-space Representation \\ of Neural Networks

### 2023-05-23 paper/main.tex
small thing

\begin{table}[!ht]
\centering
\begin{tabular}{@{}ccc@{}}
\toprule
Loss        & der 1 & der 2 \\ \midrule
binomial    &       &       \\
mse         &       &       \\
categorical &       &       \\ \bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[!ht]
\centering
\begin{tabular}{@{}ccc@{}}
\toprule
Loss        & der 1 & der 2 \\ \midrule
Bernoulli    & $\sigma(f) - y$   & $\sigma(f)(1-\sigma(f))$      \\
Mse         & $y - f$      & $1$       \\
Categorical &  $\textrm{softmax}(f_i) - y_i$     &   $\begin{bmatrix}
		p_1\\ \vdots\\p_k
	\end{bmatrix}$,     \\ \bottomrule
\end{tabular}
\end{table}
